Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-02-05 paper_jasa.tex
density derivation updated
density derivation edited

% Di: This is specific for the regression model
%Consider the hypothesis test $H_0: \beta_k=0$ against $H_1: \beta_k \ne 0$ in model \ref{multi}.
Now consider estimating the power of the visual test. Suppose $F_{|t|}(.)$ be the distribution function of an absolute value of $t$. For the regression slope parameter $\beta$ suppose the associated $p$-value be $p_B$ and from definition we have

$$p_B=Pr(|t| \ge t_{obs}| H_0)=1-F_{|t|}(t_{obs}) \Rightarrow t_{obs}=F_{|t|}^{-1}(1-p_B)$$

Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$ distribution with non-centrality parameter $\delta$. Thus the distribution function of $p-value$ be  
\begin{eqnarray}\label{dist_p}
F{p_B}(p) &=& Pr(p_B \le p)=1-Pr(1-p_B \le 1-p) \nonumber \\
  &=& 1-Pr(F_{|t|}^{-1}(1-p_B) \le F_{|t|}^{-1}(1-p) ) \nonumber \\
  &=& 1-Pr(t_{obs} \le F_{|t|}^{-1}(1-p)) \nonumber \\
  &=&\left\{ \begin{array}{ll}
          1-F_{|t|}( F_{|t|}^{-1}(1-p))=p &\mbox{ ; under $H_0$} \\
          1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
       \end{array} \right.     
\end{eqnarray}

>>>>

% Di: This is specific for the regression model
%Consider the hypothesis test $H_0: \beta_k=0$ against $H_1: \beta_k \ne 0$ in model \ref{multi}.
Now consider estimating the power of the visual test. Suppose $F_{|t|}(.)$ be the distribution function of an absolute value of $t$. For the regression slope parameter $\beta$ suppose the associated test statistic in classical test be $t_{obs}$ with $p$-value $p_B$. By definition we have

$$p_B=Pr(|t| \ge t_{obs}| H_0)=1-F_{|t|}(t_{obs}) \Rightarrow |t_{obs}|=F_{|t|}^{-1}(1-p_B)$$

Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$ distribution with non-centrality parameter $\delta$. Thus the distribution function of $p-value$ be  
\begin{eqnarray}\label{dist_p}
F{p_B}(p) &=& Pr(p_B \le p)=1-Pr(1-p_B \le 1-p) \nonumber \\
  &=& 1-Pr(F_{|t|}^{-1}(1-p_B) \le F_{|t|}^{-1}(1-p) ) \nonumber \\
  &=& 1-Pr(|t_{obs}| \le F_{|t|}^{-1}(1-p)) \nonumber \\
  &=&\left\{ \begin{array}{ll}
          1-F_{|t|}( F_{|t|}^{-1}(1-p))=p &\mbox{ ; under $H_0$} \\
          1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
       \end{array} \right.     
\end{eqnarray}
